---
title: "Sampling Continuous Mode 3"
author: "Xianbin Cheng"
date: "6/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Objective

  * This is an instruction for the continuous mode in the sampling model v3.
      + Changes since v2: We adapted some tuning, analysis, and visualization functions from the GUI
  
# Method

###1. Load libraries and source R code.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_contamination_3d.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_assay_prep.R")
source(file = "Sampling_plan.R")
source(file = "Sampling_plan_3d.R")
source(file = "Sampling_assay_3d.R")
source(file = "Sampling_assay.R")
source(file = "Sampling_outcome_3d.R")
source(file = "Sampling_outcome.R")
source(file = "Sampling_iteration.R")
source(file = "Sampling_tuning_3d.R")
source(file = "Sampling_analysis.R")
```

###2. List important parameters.

**Sampling contamination**

  * `n_contam` = the number of contamination points  
  * `x_lim` = the limits of the x-axis  
  * `y_lim` = the limits of the y-axis  
  * `geom` = the geometric shape of contamination.
      + `point` = point-source contamination
      + `area` = sporadic and systematic contamination
  * `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 
  * `bg_level` = background level of microbial contamination (CFU/g)
  * `spread_radius` = the radius of the contamination spread. 
  * `LOC` = the limit of contribution of contamination. By default, it is set at 0.001.(Both `spread_radius` and `LOC` determine the shape of decay function that describes how much contamination from the source is contributed to a target point.)
  * `fun` = the decay function that describes the spread in terms of contamination level. It can be `exp`, `norm`, or `unif`.
      + `exp` = exponential function
      + `norm` = gaussian function
      + `unif` = constant 1 (`LOC` does not affect this)

**Sampling strategies**

  * `method_sp` = sampling strategy, including `srs`, `strs`, `ss`.
  * `n_sp` = the number of sampling points
  * `n_strata` = the number of strata (applicable to *2D Stratified random sampling*)
  * `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *2D Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *2D Systematic sampling*).

**Sample Assay**
  
  * `m_sp` = individual sample size (g)
  * `method_det` = method of detection  
      + Plating: LOD = 2500 CFU/g  
      + Enrichment: LOD = 1 CFU
  * `case` = 1 ~ 15 cases that define the stringency of the sampling plan.
      + case 1 ~ 9: 3-class plans
      + case 10 ~ 15: 2-class plans
  * Attributes plans:  
      + `n` = number of analytical units 
          - `n` = 5, 10, 15, 20, 30, 60
      + `c` = maximum allowable number of analytical units yielding positive results  
      + `m` = microbial count or concentration above which an analytical unit is considered positive  
      + `M` = microbial count or concentration, if any analytical unit is above `M`, the lot is rejected.
        
**Iteration**

  * `n_iter` = the number of iterations

```{r}
## Contamination
n_contam = 1
x_lim = c(0, 20)
y_lim = c(0, 1)
lims = list(xlim = x_lim, ylim = y_lim)
prev=42
geom = "point"

cont_level = c(5, 1)
bg_level = 0.00001
spread = "continuous"
LOC = 10^(0)
fun = "unif"

# Sampling
method_sp = "ss"
n_sp = 5
n_strata = c(2,2)
by = "row"

# Assaying
case = 12
m = 0
M = 0
m_sp = 1
method_det = "enrichment"

# Iteration
n_iter = 100






#Draw each grab's cont_level following SD new_cont_level







```


##Calculate the radius using given prevalence(To add in sampling contamination)
```{r}

f_radius =function(prev,lims){
  A = x_lim[2] * y_lim[2]
  A_Circle =  A*(prev/100)
  return(R = sqrt(A_Circle/pi))
}

f_radius_approx <- function(radius,lims, prev){
  prevalence_frac = prev
  return(ifelse(radius>((y_lim[2])/2),(x_lim[2]*prev)/200,radius))
}


```

#Calculating spread_radius using given lims&prev+ set the new limit 

```{r}
spread_radius_cal = f_radius(prev,lims)
radius_approx =f_radius_approx(spread_radius_cal,lims, prev)
spread_radius=radius_approx
new_lims=list(xlim=c(radius_approx,x_lim[2]-radius_approx), ylim=c(ifelse(radius_approx<(y_lim[2]/2),radius_approx,0),ifelse(radius_approx<(y_lim[2]/2),y_lim[2]-radius_approx,y_lim[2])))
lims=new_lims
```

# Wrap arguments into one single list
```{r}
ArgList_default = list(n_contam = n_contam, lims = lims, spread = spread, spread_radius = spread_radius, 
                       cont_level = cont_level, method_sp = method_sp, n_sp = n_sp, n_strata = n_strata, 
                       by = by, LOC = LOC, fun = fun, case = case, m = m, M = M, m_sp = m_sp, 
                       method_det = method_det, bg_level = bg_level, geom = geom)

```



###3. Set a parameter for tuning and a vector of values to tune over.

  * For example, if you want to tune the parameter `n_contam`, just assign the character "n_contam" to the variable `param_name`, and then assign a vector of tuning values to the variable `vals`.
  
  * Parameters available for tuning:  
      + Continuous parameters: `n_contam`, `spread_radius`, `cont_level`, `n_sp`, `n_strata`, `LOC`, `case`, `m`, `M`, `bg_level`, `m_sp`
      + Categorical parameters: `method_sp`, `by`, `fun`, `method_det`, `geom`
      
  * Some parameters have a finite range of values. Going beyond the allowable range may not produce an error, but it will definitely produce weird results.
  
  * `seed` = the random seed for contamination locations
  
  * `n_seed` = the number of seeds.
  
```{r}
# Primary tuning parameter
var_prim = "n_contam"
vals_prim = c(1,2,3,4,5)

# Secondary tuning parameter
var_sec = "n_sp"
vals_sec = c(5, 10, 15)

# Seeds
n_seed = 1
set.seed(1)
```

###4. Tune the parameter and produce the following results:

  * `I_det` = Indicator of detection. 
      + 1 = detected
      + 0 = not detected
  * `decision` = a number that indicates lot decision. 
      + 1 = Accept lot. Microbial load < LOD.
      + 2 = Reject lot. At least 1 sample has contamination level >= M.
      + 3 = Reject lot. The number of positive samples is > c.
      + 4 = Accept lot.
  * `param` = the tuning parameter

```{r, warning = FALSE}
# 0 tuning parameter
sim_data_0 = sim_iterate2(n_seed = n_seed, n_iter = n_iter, Args = ArgList_default)
```


```{r, warning = FALSE,eval=FALSE}
# 1 tuning parameter
sim_data_1 = tune_param_n(vals = vals_prim, Args = ArgList_default, n_seed = n_seed, n_iter = n_iter, var_prim = var_prim)

# 2 tuning parameters
sim_data_2 = tune_param_sec(Args = ArgList_default, var_prim = var_prim, vals_prim = vals_prim, var_sec = var_sec, vals_sec = vals_sec)
```

5. Clean up values of probability of detection and probability of acceptance.

```{r, warning = FALSE}
data_cleaned0 = metrics_cont_0(data = sim_data_0)
```


```{r, warning = FALSE,eval=FALSE}
data_cleaned1 = metrics_cont_n(data = sim_data_1)

data_cleaned2 = metrics_cont_sec(data = sim_data_2, vals_prim = vals_prim, vals_sec = vals_sec, n_seed = n_seed)
```

# Visualization

###1. Run the model once for visualization purposes.

```{r}
# Remove unnecessary arguments
ArgList_vis = ArgList_default 
ArgList_vis[c("case", "M", "m_sp", "method_det")] = NULL
ArgList_vis$seed = 10

# Produce intermediate outputs
one_iteration = do.call(what = sim_intmed, args = ArgList_vis)
```

```{r, warning = FALSE, echo = FALSE, out.width = "50%"}
overlay_draw(method_sp = method_sp, data = one_iteration[["contam_sp_xy"]] , spread = spread, xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
contam_level_draw(dimension = "2d", method = fun, spread_radius = spread_radius, LOC = LOC)
contam_level_draw(dimension = "3d", method = fun, spread_radius = spread_radius, LOC = LOC, 
                  df_contam = one_iteration[["contam_sp_xy"]] , xlim = x_lim, ylim = y_lim, bg_level = bg_level, geom = geom)
assay_draw(data = one_iteration[["contam_sp_xy"]] , M = M, m = m, m_sp = m_sp, method_det = method_det, spread = spread, case = case)
```

###2. Visualize the probability of detection and acceptance. 

1. 0 tuning parameter

```{r}
plot_tune0(data = data_cleaned0)
```

2. 1 tuning parameter.

```{r,eval=FALSE}
plot_tune1(data = data_cleaned1, xlab = "Number of contamination points")
```

3. 2 tuning paramters.

```{r,eval=FALSE}
# Boxplot: detection probability
plot_tune2_boxplot(data = data_cleaned2, xlab = "Number of contamination points", legend_lab = "Number of samples", yvar = "P_det")

# Boxplot: acceptance probability
plot_tune2_boxplot(data = data_cleaned2, xlab = "Number of contamination points", legend_lab = "Number of samples", yvar = "Paccept")

# Ribbon plot: acceptance probability
plot_tune2_ribbon(data = data_cleaned2, xlab = "Number of contamination points", legend_lab = "Number of samples")
```


# Appendix

  * This is for the purpose of debugging only. The following functions are important intermediate functions. You may figure out which step is malfunctioning by running through these functions line by line.
  * For more info on the model framework, please refer to the function call graph in the slides "Schemes.pptx".
  
```{r, eval = FALSE}
#Calculating spread_radius using given lims&prev
spread_radius_cal = f_radius(prev,lims)
radius_approx =f_radius_approx(spread_radius_cal,lims, prev)
spread_radius=radius_approx
new_lims=list(xlim=c(radius_approx,x_lim[2]-radius_approx), ylim=c(ifelse(radius_approx<(y_lim[2]/2),radius_approx,0),ifelse(radius_approx<(y_lim[2]/2),y_lim[2]-radius_approx,y_lim[2])))
lims=new_lims

##Calculate the radius using given prevalence(To add in sampling contamination)

f_radius =function(prev,lims){
  A = x_lim[2] * y_lim[2]
  A_Circle =  A*(prev/100)
  return(R = sqrt(A_Circle/pi))
}

f_radius_approx <- function(radius,lims, prev){
  prevalence_frac = prev
  return(ifelse(radius>((y_lim[2])/2),(x_lim[2]*prev)/200,radius))
}

## Create a function to generate contamination levels. Remember that param contains log10(mean) and log10(sd). And log() in R means log(..., base = exp(1)).
f_cont_level = function(n, param){
  rlnorm(n = n, meanlog = log(10^param[1]), sdlog = log(10^param[2]))
}


# These functions produce intermediate data
contam_xy = sim_contam_new(n_contam = n_contam, lims = lims, spread = spread, 
                           spread_radius = spread_radius, cont_level = cont_level,
                           geom = geom, seed = seed)

sim_contam_new = function(geom, n_contam, c_hat, rho, m_kbar, conc_neg, lims, spread, 
                          covar, n_affected, spread_radius, cont_level, dis_level, seed){

  # Checkpoints
  stopifnot(spread %in% c("continuous", "discrete"))
  
  # Maintain the old seed and reassign the current seed with the old seed when this function ends
  # If there is no user-defined seed, the system-generated seed will be used
  old <- .Random.seed
  on.exit(expr = {.Random.seed <<- old})
  
  if(is.na(seed)){
    seed = old
    warning("Seed is not set. Contamination points won't be reproducible.")
  } else {
    set.seed(seed)
  }
  
  # Create contamination for either continuous or discrete case
  if(spread == "continuous"){
    df = sim_contam_cont(geom = geom, lims = lims, n_contam = n_contam, spread = spread, 
                         spread_radius = spread_radius, cont_level = cont_level)
    
  } else {
    df = sim_contam_dis(c_hat = c_hat, lims = lims, rho = rho, m_kbar = m_kbar, 
                        dis_level = dis_level, conc_neg = conc_neg, spread = spread, 
                        n_affected = n_affected, covar = covar)
      
  }
  
  # Remove outliers
  df2 = rm_outlier(df = df, lims = lims)
  
  # Final adjustments
  rownames(df2) = NULL
  #df2$ID = as.character(df2$ID)
  
  return(df2)
}

# A sub-function for simulation contamination for continuous case
sim_contam_cont = function(geom, lims, n_contam, spread, spread_radius, cont_level){
  
  #check point
  stopifnot(n_contam > 0 & geom %in% c("point", "area") & length(lims) == 2 & spread_radius >= 0)
  
  spot_temp = gen_contam_cont(geom = geom, n_contam = n_contam, lims = lims, 
                              spread = spread, spread_radius = spread_radius)
  df = contam_cont(spot_coord = spot_temp$spot_coord, n_contam = spot_temp$n_contam, spread = spread, 
                   spread_radius = spot_temp$spread_radius, cont_level = cont_level)
  
  return(df)
}


sp_xy = sim_plan_new(method_sp = method_sp, spread = spread, n_sp = n_sp, lims = lims, 
                     n_strata = n_strata, by = by, radius = NaN)


sim_plan_new = function(method_sp, spread, n_sp, lims, radius, n_strata, by, compartment, type, container){
  
  stopifnot(spread %in% c("continuous", "discrete"))
  
  if(spread == "continuous"){
    sim_plan_2d(method_sp = method_sp, n_sp = n_sp, xlim = lims$xlim, ylim = lims$ylim, 
                radius = radius, n_strata = n_strata, by = by)
  } else if(spread == "discrete"){
    sim_plan_3d(method_sp = method_sp, n_sp = n_sp, lims = lims, radius = radius, 
                container = container, compartment = compartment, type = type, n_strata = n_strata, by = by)
  }
}

dist_contam_sp = calc_dist(df_contam = contam_xy, df_sp = sp_xy, spread = spread, 
                           method_sp = method_sp)
contam_sp_xy = gen_sim_data_new(df_contam = contam_xy, df_sp = sp_xy, dist = dist_contam_sp, 
                                spread = spread, spread_radius = spread_radius, LOC = LOC, 
                                bg_level = bg_level, fun = fun, geom = geom)


# Create a function that calculates contamination levels for each sample point and combine "contam_xy" and "sp_xy"
gen_sim_data_new = function(df_contam, df_sp, dist, spread, spread_radius, LOC, bg_level,
                            fun, L, rho, m_kbar, sp_radius, conc_neg, geom, method_sp, lims){
  
  stopifnot(spread %in% c("continuous", "discrete"))

  ### Combine everything, fill the NAs with the corresponding contamination level.
  df = rbind(df_contam, df_sp)
  
  if(spread == "continuous"){
    
    # Area-based: update spread_radius and fun
    stopifnot(geom %in% c("point", "area"))
    if(geom == "area"){
      spread_radius = df_contam[["r"]]
    }
    
    # Calculate the sample concentration in a continuous case
    a = calc_level_cont(df_contam = df_contam, dist = dist, spread_radius = spread_radius, 
                        LOC = LOC, fun = fun, bg_level = bg_level)
    
    # Update the cont_level column for the sample points.
    df$cont_level[match(x = a$ID_sp, table = df$ID)] = a$cont_level 
    
    return(df)
    
  } else if (spread == "discrete") {
    
    b = get_pooled_sample(df_contam = df_contam, df_sp = df_sp, dist = dist, 
                          method_sp = method_sp, L = L, rho = rho, 
                          m_kbar = m_kbar, sp_radius = sp_radius, conc_neg = conc_neg, lims = lims)
    
    c = calc_true_contam(df_contam = df_contam, rho = rho, lims = lims, m_kbar = m_kbar, conc_neg = conc_neg)
    
    return(list(combined = df, raw = b, c_true = c)) 
  }
}
cover = calc_cover(df_dist = dist_contam_sp, spread_radius = spread_radius, 
                   spread = spread, geom = geom, df_contam_sp = contam_sp_xy)
decision = lot_decision_new(data = contam_sp_xy, case = case, m = m, M = M, 
                            spread = spread, method_det = method_det, m_sp = m_sp)
words(x = decision)

# This function produces the dataframe "contam_sp_xy" and the distance dataframe
test1 = sim_intmed(n_contam = n_contam, lims = lims, spread = spread, spread_radius = spread_radius, 
                   method_sp = method_sp, n_sp = n_sp, n_strata = n_strata, by = by, LOC = LOC, 
                   fun = fun, cont_level = cont_level, bg_level = bg_level, geom = geom, seed = seed)

# This function produces two values: I_det and decision
test2 = sim_outcome_new(n_contam = n_contam, lims = lims, spread = spread, spread_radius = spread_radius, 
                       method_sp = method_sp, n_sp = n_sp, n_strata = n_strata, by = by, LOC = LOC, 
                       fun = fun, cont_level = cont_level, bg_level = bg_level, case = case, m = m, 
                       M = M, method_det = method_det, geom = geom, m_sp = m_sp, seed = seed)

# This function produces a sim_outcome_new() function with all the input parameters loaded
test3 = gen_sim_outcome_new(n_contam = n_contam, lims = lims, spread = spread, spread_radius = spread_radius, 
                       method_sp = method_sp, n_sp = n_sp, n_strata = n_strata, by = by, LOC = LOC, 
                       fun = fun, cont_level = cont_level, bg_level = bg_level, case = case, m = m, 
                       M = M, method_det = method_det, geom = geom, m_sp = m_sp, seed = seed)

# First layer of iteration: This function iterates the sim_outcome_new() for n_iter times with the same contamination locations
test4 = sim_iterate(n_iter = n_iter, Args = ArgList_default, seed = seed)

# Second layer of iteration: Iterate the 1st layer with different seeds
test5 = sim_iterate2(n_seed = n_seed, n_iter = n_iter, Args = ArgList_default)

# Tuning layer (tune over a value of the primary tuning parameter)
test6 = tune_param(Args = ArgList_default, n_seed = n_seed, n_iter = n_iter, param = "n_contam", val = 100)

# tune_param_n()

# tune_param_sec()
```

```{r, echo = TRUE}
sessionInfo()
```

